Network packet generation for Artificial Intelligence\\

### 2020-02-27 paper1/paper1.tex
Implemented feedback from Boris III

Cyber -attacks generally try to exploit various vulnerabilities and carry out malicious actions. In order to provide an overview of the multitude of different attack methods, there are various approaches in the literature to classify the attacks into a few groups. The focus of this work is the classification model found in  \cite{b5}, which aims to enable a holistic view of attacks. Basically, nine different attack classes are described, including network attacks, denial of service attacks, information gathering attacks and various types of malware-based attacks. Subsequently, various attack targets (software, hardware and network), as well as vulnerabilities (in design, implementation, configuration) are explained in more detail.
Tools for carrying out-cyber attacks are basically divided into two different groups, namely information gathering tools and attack launching tools. The former tries to find out various information about the system to be attacked (open ports, operating system used, etc.). Sniffing and scanning tools can be used for this. Attack launching tools for performing denial of service attacks and for packet forging were identified. Furthermore, it is also possible to proceed on the basis of legitimate requests on the application layer. The creation of realistic network traffic based on benign and malicious data packets is a complex undertaking. By using tools, various strategies exist to generate harmless traffic, for example by using software robots.

>>>>

Cyber-attacks generally try to exploit various vulnerabilities and carry out malicious actions. In order to provide an overview of the multitude of different attack methods, there are various approaches in the literature to classify the attacks into a few groups. The focus of this work is the classification model found in  \cite{b5}, which aims to enable a holistic view of attacks. Basically, nine different attack classes are described, including network attacks, denial of service attacks, information gathering attacks and various types of malware-based attacks. Subsequently, various attack targets (software, hardware and network), as well as vulnerabilities (in design, implementation, configuration) are explained in more detail.
Tools for carrying out cyber-attacks are basically divided into two different groups, namely information gathering tools and attack launching tools. The former try to find out various information about the system to be attacked (open ports, operating system used, etc.). Sniffing and scanning tools can be used for this. Attack launching tools for performing denial of service attacks and for packet forging were identified. Furthermore, it is also possible to proceed on the basis of legitimate requests on the application layer. The creation of realistic network traffic based on benign and malicious data packets is a complex undertaking. By using tools, various strategies exist to generate harmless traffic, for example by using software robots.
